---
title: "Assignment_607_1"
author: "Pei-Ming Chen"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(plyr)
```

### Introduction
https://projects.fivethirtyeight.com/2022-election-forecast/
https://github.com/fivethirtyeight/data/tree/master/election-forecasts-2022
The loaded senator data was from these two websites. 

```{r load_senator_data}
mydata <-read.csv("https://raw.githubusercontent.com/PMCformosa/Data607_Lab01/main/senate_steps_2022.csv", sep=",")
```


### Rename Column

Headers of the table were re-phrase in a much easier understood one 

```{r rename_column}
mydata <- rename(mydata, c("candidateA"="Candidate_A", "candidateB"="Candidate_B","displaystep"="Calculation_Step"))
```


### Subset data

The first step of displaystep of the Candidatess with margin between -5 to 5 were chosen. 

```{r plot-prop-boys-arbuthnot}
subset(mydata, (margin > -5 & margin < 5) & Calculation_Step==1, select = c(branch, district, forecastdate, margin, Candidate_A, Candidate_B))
```

### Conclusion

I chose the data column that most people interest in the senator election. The purpose is to let people understand this piece of data much easier. 


